Reading Notes

### 2020-07-28 reading-notes.tex
read yang2006

\cite{Yang2006a}
\cite{McCoy1998a}
\bibliography{library}
\bibliographystyle{ieeetr}
\end{document}

>>>>

\cite{Yang2006a}
reduced models include solvent in the effective parameters. Amber UA for proeins. groups hydrogens with carbons except on backbone. United atom model dates back to 1970s the UNICEPP ff. nonpolar hydrogens are implicit. efficiency gain is. system size can reduce by roughly half since many hydrogens in biological/organic systems. fewer nonbonded and internal dof. larger dynamics step sizes since small hydrogen mass requires a smaller time step. and hydrogen position is not usually helpful for analysis methods like x-ray crystallography. 
by representing polar hydrogens this model can gain the benefits of UA while minimizing some disadvantages like UA ff not representing h-bonding or pi-stacking.

\cite{Levitt1976}
one cg bead per residue

\cite{McCoy1998a}
\bibliography{library}
\bibliographystyle{ieeetr}
\end{document}
